Prag Bat Summary

### 2022-02-08 analysis/summary.Rmd
add bfcs models

library(tidyverse)
library(knitr)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
#library(psych)
library(readODS)
#library(brms)
library(psy)
library(tidyboot)
library(lubridate)
library(ggpubr)
library(lavaan)
library(blavaan)
library(tidySEM)
library(semPlot)
```

@@

```{r}
fit <- bcfa(model, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)

saveRDS(fit, "../saves/bcfa_prag")

fit2 <- bcfa(model2, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)

saveRDS(fit2, "../saves/bcfa_single")

fit3 <- bcfa(model3, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)

saveRDS(fit3, "../saves/bcfa_separate")
```

```{r}
blavCompare(fit, fit2)

blavCompare(fit, fit3)

blavInspect(fit, "lvs")
```

```{r}
#model weights
w1 <- exp(-0.5*0)/(exp(-0.5*0)+exp(-0.5*6.7)+exp(-0.5*7.1)+exp(-0.5*8.9))
```

>>>>

library(tidyverse)
library(knitr)
library(ggthemes)
library(jsonlite)
library(readxl)
library(corrr)
library(corrplot)
library(ggcorrplot)
library(reshape2)
#library(psych)
library(readODS)
#library(brms)
library(psy)
library(tidyboot)
library(lubridate)
library(ggpubr)
library(lavaan)
library(blavaan)
#library(tidySEM)
#library(semPlot)
```

@@

```{r}
# fit <- bcfa(model, data = semd, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
# saveRDS(fit, "../saves/bcfa_prag.rds")
fit <- readRDS("../saves/bcfa_prag.rds")

# fit2 <- bcfa(model2, data = semd, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
# saveRDS(fit2, "../saves/bcfa_single.rds")
fit2 <- readRDS("../saves/bcfa_single.rds")

# fit3 <- bcfa(model3, data = semd, bcontrol = list(cores = 4), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)
# saveRDS(fit3, "../saves/bcfa_separate.rds")
fit3 <- readRDS("../saves/bcfa_separate.rds")
```

```{r}
# blavCompare(fit, fit2)
# 
# blavCompare(fit, fit3)

```{r}
# fit_waic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "waic")%>%pull(value)
# fit2_waic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "waic")%>%pull(value)
# fit3_waic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "waic")%>%pull(value)
# 
# fit_se_waic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "se_waic")%>%pull(value)
# fit2_se_waic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "se_waic")%>%pull(value)
# fit3_se_waic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "se_waic")%>%pull(value)
# 
# fit_looic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "looic")%>%pull(value)
# fit2_looic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "looic")%>%pull(value)
# fit3_looic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "looic")%>%pull(value)
# 
# fit_se_looic <- fitmeasures(fit)%>%as_tibble(rownames = "index")%>%filter(index == "se_loo")%>%pull(value)
# fit2_se_looic <- fitmeasures(fit2)%>%as_tibble(rownames = "index")%>%filter(index == "se_loo")%>%pull(value)
# fit3_se_looic <- fitmeasures(fit3)%>%as_tibble(rownames = "index")%>%filter(index == "se_loo")%>%pull(value)
# 
# #model weights
# ## waic
# w1 <- exp(-0.5*(fit_waic-fit_waic))/(exp(-0.5*(fit_waic-fit_waic))+exp(-0.5*(fit2_waic-fit_waic))+exp(-0.5*7.1)+exp(-0.5*(fit3_waic-fit_waic)))
# w2 <- exp(-0.5*(fit2_waic-fit_waic))/(exp(-0.5*(fit_waic-fit_waic))+exp(-0.5*(fit2_waic-fit_waic))+exp(-0.5*7.1)+exp(-0.5*(fit3_waic-fit_waic)))
# w3 <- exp(-0.5*(fit3_waic-fit_waic))/(exp(-0.5*(fit_waic-fit_waic))+exp(-0.5*(fit2_waic-fit_waic))+exp(-0.5*7.1)+exp(-0.5*(fit3_waic-fit_waic)))
# ## looic
# l1 <- exp(-0.5*(fit_looic-fit_looic))/(exp(-0.5*(fit_looic-fit_looic))+exp(-0.5*(fit2_looic-fit_looic))+exp(-0.5*7.1)+exp(-0.5*(fit3_looic-fit_waic)))
# l2 <- exp(-0.5*(fit2_looic-fit_looic))/(exp(-0.5*(fit_looic-fit_looic))+exp(-0.5*(fit2_looic-fit_looic))+exp(-0.5*7.1)+exp(-0.5*(fit3_looic-fit_waic)))
# l3 <- exp(-0.5*(fit3_looic-fit_looic))/(exp(-0.5*(fit_looic-fit_looic))+exp(-0.5*(fit2_looic-fit_looic))+exp(-0.5*7.1)+exp(-0.5*(fit3_looic-fit_waic)))
# 
# model_comparison <- tibble(
#   model = c("fit1", "fit2", "fit3"),
#   waic = c(fit_waic, fit2_waic, fit3_waic), 
#   waic_se = c(fit_se_waic, fit2_se_waic, fit3_se_waic), 
#   waic_weight = c(w1, w2, w3),
#   looic = c(fit_looic, fit2_looic, fit3_looic),
#   looic_se = c(fit_se_looic, fit2_se_looic, fit3_se_looic),
#   looic_weight = c(l1, l2, l3)
# )%>%
#   arrange(waic)%>%
#   write_csv(., "../saves/bcfa_model_comparison.csv")

model_comparison <- read_csv("../saves/bcfa_model_comparison.csv")
```
